Visualizations for the manuscript

### 2022-06-22 metanalysis_visualization/manuscript_Figures.Rmd
figures minor corrections for axis labels and format on the ITS plot

ci_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[", as.character(round(`2.5%`, 2)), "; ", as.character(round(`97.5%`, 2)), "]"))

@@

@@

```{r}
plot_annotations_df_primary <- pvalues_boot %>%
  select(siteid, label) %>% 
  filter(term == "difference_slope") %>% 
  left_join(country_map)
```

```{r}
ggplot(bootstrapped_fitted_all,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom") 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

```{r}
pvalues_boot %>% 
  inner_join(ci_boot) %>% 
  inner_join(country_map) %>% 
  arrange(plotsLabel) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  select(plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

@@

ci_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[", as.character(round(`2.5%`, 2)), "; ", as.character(round(`97.5%`, 2)), "]"))

@@

```{r}
pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-3), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r}
plot_annotations_sex_df <- pvalues_boot_sex %>%
  select(term, sex, label) %>% 
  filter(term == "difference_slope" & sex == "female") %>% 
  mutate(plotsLabel = "Female")

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

ci_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[", as.character(round(`2.5%`, 2)), "; ", as.character(round(`97.5%`, 2)), "]"))

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "Number of ICD-10 codes") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
ggsave("figure_supp2_ICDdictionaryQC.png", height = 20, width = 45, units = "cm")

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("figure_supp1A_counts_per_site.png",counts_plot, height = 20, width = 32, units = "cm")

@@

counts_agg2plot <- counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_agg2plot
ggsave("figure_supp1B_counts_all.png",counts_agg2plot, height = 20, width = 32, units = "cm")

>>>>

ci_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), "]"))

@@

```{r}
pvalues_boot_complete <- pvalues_boot %>% 
  inner_join(ci_boot) %>% 
  inner_join(country_map) %>% 
  arrange(plotsLabel) %>% 
  mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  select(plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

```{r}
#plot_annotations_df_primary <- pvalues_boot %>%
#  select(siteid, label) %>% 
#  filter(term == "difference_slope") %>% 
#  left_join(country_map)

plot_annotations_df_primary <- pvalues_boot_complete %>%
  select( siteid, label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel )%>% 
  left_join(country_map)

@@

```{r}
ggplot(bootstrapped_fitted_all,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

ci_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), "]"))

@@

```{r}
pvalues_boot_sex_complete <- pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-3), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r}
#plot_annotations_sex_df <- pvalues_boot_sex %>%
#  select(term, sex, label) %>% 
#  filter(term == "difference_slope" & sex == "female") %>% 
#  mutate(plotsLabel = "Female")

plot_annotations_sex_df <- pvalues_boot_sex_complete %>%
  filter( sex == "female") %>% 
    mutate(plotsLabel = "Female") %>%
  select( label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel )

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

ci_boot_disorders <- bootstrapped_coefficients_disorders %>% 
  group_by(disorder_group, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), "]"))

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" , ncol = 3) +
  labs(x ="site identifier", y = "Number of ICD-10 codes") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 11), 
        strip.text = element_text(size = 13), 
        axis.text.y = element_text(size = 11), 
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 13), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.title=element_text(size=13), 
        legend.text=element_text(size=13), 
        legend.position="bottom") 
ggsave("figure_supp2_ICDdictionaryQC.png", height = 40, width = 45, units = "cm")

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("figure_supp1A_counts_per_site.png",counts_plot, height = 25, width = 40, units = "cm")

@@

counts_agg2plot <- counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_agg2plot
ggsave("figure_supp1B_counts_all.png",counts_agg2plot, height = 20, width = 32, units = "cm")
